R for Clinical Study Reports and Submission

### 2021-11-11 tlf-disposition.Rmd

```{r}
adsl <- read_sas("adam_data/adsl.sas7bdat")
```

@@

- USUBJID: Unique subject identifier
- TRT01P: Planed treatment
- TRT01PN: Planned treatment numeric encoding
- DISCONFL: Discontinued from study flag
- DCREASCD: Discontinued from study reason coded

>>>>

```{r}
adsl <- read_sas("data-adam/adsl.sas7bdat")
```

@@

- USUBJID: Unique subject identifier
- TRT01P: Planned treatment
- TRT01PN: Planned treatment numeric encoding
- DISCONFL: Discontinued from study flag
- DCREASCD: Discontinued from study reason coded

### 2021-11-11 tlf-overview.Rmd

In clinical trials, a critical step is submission to regulatory agencies.
[Electronic Common Technical Document (eCTD)](https://en.wikipedia.org/wiki/Electronic_common_technical_document)
has become a worldwide regulatory submission standard format.
For example, the United States Food and Drug Administration (US FDA) required
new drug applications and biologics license applications
[must be submitted using the eCTD format](https://www.fda.gov/drugs/electronic-regulatory-submission-and-review/electronic-common-technical-document-ectd).
The Clinical Data Interchange Standards Consortium (CDISC) provided a
[pilot project following ICH E3 guidance](https://bitbucket.cdisc.org/projects/CED/repos/sdtm-adam-pilot-project/browse).

@@

Building CSRs is teamwork between clinicians, medical writers, statisticians, statistical programmers,
and other relevant specialists such as experts on biomarkers.
Here, we focus on the work and deliverables completed by statisticians and statistical programmers.
In an organization, they commonly work together to
define, develop, validate and deliver tables, listings, and figures (TLFs) required for a CSR to
summarize the safety and/or safety of the pharmaceutical product.
Microsoft Word is widely used to prepare CSR in the pharmaceutical industry.
Therefore, `rtf`, `doc`, `docx` are commonly used formats in their deliverables.

@@

We provided a brief introduction of `r2rtf` and showed how to transfer
data frames into Table, Listing, and Figures (TLFs).

>>>>

In clinical trials, a critical step is to submit trial results to regulatory agencies.
[Electronic Common Technical Document (eCTD)](https://en.wikipedia.org/wiki/Electronic_common_technical_document)
has become a worldwide regulatory submission standard format.
For example, the United States Food and Drug Administration (US FDA) required
new drug applications and biologics license applications
[must be submitted using the eCTD format](https://www.fda.gov/drugs/electronic-regulatory-submission-and-review/electronic-common-technical-document-ectd).
The Clinical Data Interchange Standards Consortium (CDISC) provided a
[pilot project following ICH E3 guidance](https://bitbucket.cdisc.org/projects/CED/repos/sdtm-adam-pilot-project/browse).

@@

Building CSRs is teamwork between clinicians, medical writers, statisticians, statistical programmers,
and other relevant specialists such as experts on biomarkers.
Here, we focus on the work and deliverables completed by statisticians and statistical programmers.
In an organization, they commonly work together to
define, develop, validate and deliver tables, listings, and figures (TLFs) required for a CSR to
summarize the efficacy and/or safety of the pharmaceutical product.
Microsoft Word is widely used to prepare CSR in the pharmaceutical industry.
Therefore, `.rtf`, `.doc`, `.docx` are commonly used formats in their deliverables.

@@

We provide a brief introduction of `r2rtf` and showed how to transfer
data frames into table, listing, and figures (TLFs).
